How to Write Theses\\ With Two Line Titles

### 2019-08-07 chapters/litReview/MRMLalgo.tex
new

\section{Testing Machine Learning Programs}
\subsection{Properties of Machine Learning Applications for Use in Metamorphic Testing \cite{Murphy}}
In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. Non-testable programs can be tested in one of the two ways:
\begin{itemize}
  \item Creating multiple implementations of the same program and testing them on same inputs and comparing the results. If the outputs are not same then either of the implementations can contain error. This approach is called pseudo-oracle.
  \item In absence of multiple oracle, metamorphic testing can be used. In metamorphic testing, the input is modified using a metamorphic relation such that the two sets of input will generate similar outputs. If similar outputs are not observed then there must be a defect.
\end{itemize}
The main challenge with metamorphic testing is to come up with the metamorphic relations to transform inputs since such coming up with such relations require domain knowledge and/or familiarity with the implementation.
In this paper the authors seek to create a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning softwares. These set of properties can be applied to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications. The problem with some of the current machine learning frameworks like: Weka and Orange is that they compare the quality of results but don’t evaluate the correctness of the results. The authors apply metamorphic testing to three ML applications: MartiRank, SVM-Light, PAYL.
MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model. The algorithm then performs similar operations from the model on the test data to produce a ranking list. SVM-Light is an open-source implementation of SVM that also has a ranking mode. The authors also investigated an intrusion detection system called PAYL. PAYL is an unsupervised machine learning system. It’s dataset simply consist of TCP/IP network payloads(stream of bytes) without any label or classification.
Based on the analysis of MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model. Thus, adding a constant value to every attribute or multiplying each attribute with a positive number, should not affect the model and generate the same ranking as before. Thus, the metamorphic properties identified were: addition and multiplication. Applying the model on two sets of data, one of which created from the other, either by multiplying a positive number or, adding a constant number, should not change the ranking. Changing the order of examples should not affect the model or ranking since the algorithm sorts the inputs thus, MartiRank also has permutative metamorphic property. Multiplying the data by a negative constant value will create a new sorting order which can easily predicted. The only change to the model will be the sorting direction i.e. the algorithm will change the sorting direction but keep the sorting order intact. Thus, MartiRank also displays an invertive metamorphic property where the output can be predicted by taking the opposite of input. MartiRank also includes inclusive and exclusive metamorphic properties. Knowing the model can help predict the position of any new elements.

\subsection{Application of Metamorphic Testing to Supervised Classifiers \cite{Xie2009}}
Building on the previous paper, the authors explore the metamorphic relations based on expected behavior of given machine learning problems. They present a case study on Weka, a popular machine learning framework, which is also the foundation for computational science tools such as BioWeka in bioinformatics. In this paper the authors explore k-Nearest Neighbors and Naive Bayes classifier algorithms. Previously, they researched on Support Vector Machines.
In this paper the authors seek to identify the metamorphic relations for the two algorithms (kNN and NBC). NBC and kNN both calculates the mean and standard deviation of the input data. Thus, the metamorphic relations identified are:
Permuting the order of input data does not affect the mean or standard deviation.
Multiplying the data with -1 does not affect the standard deviation since, the deviation from the mean will still be the same.
Multiplying the data with some other positive number will increase the standard deviation by the same amount. Thus, the output will still be predictable.
The authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
\begin{enumerate}
  \item Consistency with affine transformation.
  \item Permutation of class labels.
  \item Permutation of attributes.
  \item Addition of uninformative/informative attributes.
  \item Consistency with re-prediction.
  \item Addition of training samples.
  \item Addition of classes by duplicating/re-labeling samples.
  \item Removal of classes/samples.
\end{enumerate}
Next, the authors introduce the notion of validation and verification. Validation refers to choosing the most appropriate algorithm to solve a problem. Verification refers to whether the implemented algorithm is correct or not. Current, software testing methods have not addressed the problem of validation and only focus on verification.
The authors then performed an experiment to verify the correctness of Weka. They created a set of random input data and used the above metamorphic relationships to generate another set of inputs. Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithm. It was observed that several MRs violated NBC algorithms. Violations in the MRs that are necessary properties imply defects in implementation. In the case of kNN algorithm, none of the necessary MRs were violated which means that there are no implementation error as per the testing.

@@

>>>>

\section{Testing Machine Learning Programs}
Performing metamorphic testing require domain knowledge and/or familiarity with the implementation to be able to come up with the metamorphic relations in order to transform inputs.
\subsection{Properties of Machine Learning Applications for Use in Metamorphic Testing \cite{Murphy2008}}
In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. Non-testable programs can be tested in one of the two ways:
\begin{itemize}
  \item Creating multiple implementations of the same program and testing them on same inputs and comparing the results. If the outputs are not same then either of the implementations can contain error. This approach is called pseudo-oracle.
  \item In absence of multiple oracle, metamorphic testing can be used. In metamorphic testing, the input is modified using a metamorphic relation such that the two sets of input will generate similar outputs. If similar outputs are not observed then there must be a defect.
\end{itemize}
STU

Murphy, Kaiser, Hu, and, Wu (2008) created a taxonomy of metamorphic relationships that can be applied to the input data for both supervised and unsupervised machine learning software. These set of properties can be used to define the metamorphic relationships so that metamorphic testing can be used as a general testing method for machine learning applications\cite{Murphy2008}. Similar work has also been done by Xie et al.(2009) where they identified metamorphic relations for k-nearest neighbors algorithm (k-NN) and naïve Bayes classifier (NBC).
Murphy et al. investigated two supervised algorithms MartiRank and SVM-Light and an unsupervised system PAYL to identify basic metamorphic properties in machine learning algorithms.

The problem with some of the current machine learning frameworks like: Weka and Orange is that they compare the quality of results but don’t evaluate the correctness of the results. The authors apply metamorphic testing to three ML applications: MartiRank, SVM-Light, PAYL.
MartiRank is a supervised ML algorithm that applies segmentation and sorting of the input data to create a model. The algorithm then performs similar operations from the model on the test data to produce a ranking list. SVM-Light is an open-source implementation of SVM that also has a ranking mode. The authors also investigated an intrusion detection system called PAYL. PAYL is an unsupervised machine learning system. It’s dataset simply consist of TCP/IP network payloads(stream of bytes) without any label or classification.
Based on the analysis of MartiRank algorithm, the authors realized that the actual values of the attributes were not very important but their relative values determined the model. Thus, adding a constant value to every attribute or multiplying each attribute with a positive number, should not affect the model and generate the same ranking as before. Thus, the metamorphic properties identified were: addition and multiplication. Applying the model on two sets of data, one of which created from the other, either by multiplying a positive number or, adding a constant number, should not change the ranking. Changing the order of examples should not affect the model or ranking since the algorithm sorts the inputs thus, MartiRank also has permutative metamorphic property. Multiplying the data by a negative constant value will create a new sorting order which can easily predicted. The only change to the model will be the sorting direction i.e. the algorithm will change the sorting direction but keep the sorting order intact. Thus, MartiRank also displays an invertive metamorphic property where the output can be predicted by taking the opposite of input. MartiRank also includes inclusive and exclusive metamorphic properties. Knowing the model can help predict the position of any new elements.

\subsection{Application of Metamorphic Testing to Supervised Classifiers \cite{Xie2009}}
Building on the previous paper, the authors explore the metamorphic relations based on expected behavior of given machine learning problems. They present a case study on Weka, a popular machine learning framework, which is also the foundation for computational science tools such as BioWeka in bioinformatics. In this paper the authors explore k-Nearest Neighbors and Naive Bayes classifier algorithms. Previously, they researched on Support Vector Machines.
In this paper the authors seek to identify the metamorphic relations for the two algorithms (kNN and NBC). NBC and kNN both calculates the mean and standard deviation of the input data. Thus, the metamorphic relations identified are:
Permuting the order of input data does not affect the mean or standard deviation.
Multiplying the data with -1 does not affect the standard deviation since, the deviation from the mean will still be the same.
Multiplying the data with some other positive number will increase the standard deviation by the same amount. Thus, the output will still be predictable.
From the study of these algorithms, the authors then, define the metamorphic relations that a classification algorithm is expected to exhibit:
\begin{enumerate}
  \item Consistency with affine transformation.
  \item Permutation of class labels.
  \item Permutation of attributes.
  \item Addition of uninformative/informative attributes.
  \item Consistency with re-prediction.
  \item Addition of training samples.
  \item Addition of classes by duplicating/re-labeling samples.
  \item Removal of classes/samples.
\end{enumerate}
Next, the authors introduce the notion of validation and verification. Validation refers to choosing the most appropriate algorithm to solve a problem. Verification refers to whether the implemented algorithm is correct or not. Current, software testing methods have not addressed the problem of validation and only focus on verification.
The authors then performed an experiment to verify the correctness of Weka. They created a set of random input data and used the above metamorphic relationships to generate another set of inputs. Upon running the inputs on both the algorithms they realized only a subset of MRs were a necessary property of the corresponding algorithm. It was observed that several MRs violated NBC algorithms. Violations in the MRs that are necessary properties imply defects in implementation. In the case of kNN algorithm, none of the necessary MRs were violated which means that there are no implementation error as per the testing.

@@

\cite{Segura2016}
Composition of Metamorphic Relations (CMR) can be used to construct new metamorphic relations by combining several existing relations. The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions. Two metamorphic relations are considered “compositable” if the follow-up test cases of one of the relations can always be used as source test case of the other. The composition is sensitive to the order of metamorphic relations and generalizable to any number of them. Determining whether two metamorphic relations are composable is a manual task. Chen et al. \cite{Chen2016} presented a specification–based tool called METRIC for the identification of metamorphic relations. In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames. The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.

### 2019-08-07 chapters/litReview/finalLit.tex
new

\section{Software testing}
Testing is one of the most important activity in software development life cycle. Bertolino define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions". Testing is widely used in industry for quality assurance purposes. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code developers, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service. Some studies (B. Beizer) have estimated that software testing can use upto fifty percent, or more, of the total development cost. Thus, it is program software testing is worthy of our attention for research and improvement. 
Weyuker (1982) categorizes the testing research activities into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}

However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs. These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, the two fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle. (Chen, Tse, & Zhou Semi Proving: An integrated method and Elbaum2014)

 One of the first problems that testers run into is that they don't have access to acceptable output to test the program output against. This problem is often referred to as the Oracle problem. Weyuker (1982) provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts. As per Weyuker, non-testable programs can be defined as the programs for which such oracles do not exist. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.

 One way of elevating the oracle-problem is through the use of pseudo oracle. It is also referred to as dual-coding and used in higly critical software. (Weyuker and automatic system testing of programs without test oracles: Christian murphy, kuang shen). Pseudo-oracles are multiple implementation of same specification of the original program under test.
 However dual coding comes with it's own set of problems. As [this and this ] pointed out that it 
 multiple implementation may not exist
 multiple implementation may be created by the same or same set of developers prone to make same mistakes.
 pseudo-oracle requires at least two implementation and it may be a lot of overhead 
 The authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

 Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}

Many techniques have since been developed to develop these set of non-testable programs.

Two ways to deal with uncertainty are to exercise more control over the inputs provided to the unit under test and to constrain the testing environment. Some uncertainties like those present in systems that deal with the physical world are aleatoric; that is, they cannot be known precisely because of their inherent variability and noise.  Epistemic uncertainties are those that could be resolved with enough effort (e.g., over-engineering a sensor-based system to minimize inference errors about the environment)— and resolving them are becoming more numerous and costly, as the systems are becoming increasingly complex. A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time. The authors provide a set of requirements for adequate handling of uncertainty in testing:
\begin{enumerate}
  \item Specifying input distributions and generating inputs with the help of the distributions instead of using discrete inputs.
  \item Probabilistic oracles that can help distinguish acceptable from unacceptable misbehaviors. These models will also provide the specification of the likelihood of results.
  \item Richer models to represent system and environment uncertainty, so that uncertainties can be connected to test requirements and outcomes. This will help with automated uncertainty quantification.
\end{enumerate}
Not all systems will impose these requirements, and not all techniques will satisfy them. In fact, they expect it will be necessary to develop a suite of techniques for dealing with uncertainty, selected according to system characteristics and the particular forms of uncertainty the system embodies and based on the use of stochastic models and quantitative analyses.

\section{On Testing Non-testable Programs \cite{Weyuker}}

 But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation. 
A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors.

Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer. In such cases, we make use of partial oracles. It is relatively easier to test the systems on simpler inputs for which the output is known. There is rarely a single correct answer in these types of computations. Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution. The authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

>>>>

\section{Software testing}
Testing is one of the most important activity in software development life cycle. Bertolino (2007) define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions". Testing is widely used in industry for quality assurance purposes. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service, etc.\cite{Bertolino2007} A study by Beizer (2006) has estimated that software testing can use up to fifty percent, or more, of the total development cost. Thus, it is clear that program software testing is worthy of our attention for research and improvement.\cite{Beizer1990} 
Weyuker (1982) categorizes the testing research activities into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}

However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs. These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, the two fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle. \cite{Chen2002} \cite(Elbaum2014)
Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}\cite{Weyuker}

 One of the first problems that testers run into is that they don't have access to acceptable output to test the program output against. This problem is often referred to as the Oracle problem. Weyuker provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts. As per Weyuker, non-testable programs can be defined as the programs for which such oracles do not exist. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.\cite{Weyuker}

 A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time.\cite(Elbaum2014)

 Many techniques have since been developed to test these set of non-testable programs. One way of elevating the oracle-problem is through the use of pseudo oracle. It is also referred to as dual-coding and is used in highly critical software.\cite{Weyuker}\cite{Murphy2009}. Pseudo-oracles are multiple implementation of same specification of the original program under test.
 However, dual coding comes with it's own set of problems. As the authors [this and this ] pointed out that pseudo-oracle requires at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
 In light of shortcomings of the testing process the authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.\cite(Weyuker)

But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation.  
A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors. \cite{Weyuker}

Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer. In such cases, we make use of partial oracles. It is relatively easier to test the systems on simpler inputs for which the output is known. There is rarely a single correct answer in these types of computations. Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution.

### 2019-08-07 chapters/litReview/metamorphicTesting.tex
new

Zhou et al. (Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H. Huang‡, T.H. Tse§,
Zongyuan Yang ¶, Haitao Huang ¶, and T. Y. Chen ‡) argued that successful test cases

Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to answer the oracle problem.
Segura et al. did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing.
% \begin{enumerate}
% 	\item RQ1: What improvements to the technique have been made?
% 	\item RQ2: What are its known application domains?
% 	\item RQ3: How are experimental evaluations performed?
% 	\item RQ4: What are the future research challenges?
% \end{enumerate}

\section{Metamorphic Testing}
	\subsection{A Survey on Metamorphic Testing \cite{Segura2016}}

		\subsubsection{Properties of good metamorphic relations}
			To answer the first question they first studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
			\begin{itemize}
				\item A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.
				\item Metamorphic relations that make execution of the follow–up test case as different as possible from the source test case.
				\item Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.
				\item Formally described metamorphic relations. In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow–up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
			\end{itemize}

		\subsubsection{Construction of metamorphic relations}
		Composition of Metamorphic Relations (CMR) can be used to construct new metamorphic relations by combining several existing relations. The rationale behind this method is that the resulting relations should embed all properties of the original metamorphic relations, and thus they should provide similar effectiveness with a fewer number of metamorphic relations and test executions. Two metamorphic relations are considered “compositable” if the follow-up test cases of one of the relations can always be used as source test case of the other. The composition is sensitive to the order of metamorphic relations and generalizable to any number of them. Determining whether two metamorphic relations are composable is a manual task. Chen et al. \cite{Chen2016} presented a specification–based tool called METRIC for the identification of metamorphic relations. In this framework, the program specification is used to partition the input domain in terms of categories, choices and complete test frames. The results of an empirical study with 19 participants suggest that METRIC is effective and efficient at identifying metamorphic relations.

		\subsubsection{Generation of source test cases}
		Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations. Given the source code of a program written in C and a metamorphic relation, AMT tries to find test cases that violate the relation. The underlying method is based on the translation of the code into an equivalent constraint logic program over finite domains. Other techniques like “special values” and random testing can also be used as source test cases for metamorphic testing. Genetic algorithms have also been used for the selection of source test cases, to maximize the paths traversed in the program under test.

		\subsubsection{Execution of metamorphic test cases}
		The execution of a metamorphic test case is typically performed in two steps. First, a follow–up test case is generated by applying a transformation to the inputs of a source test case. Second, source and follow–up test cases are executed, checking whether their outputs violate the metamorphic relation. \par
		Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively. In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow–up test case of each metamorphic relation as the source test case of the next metamorphic relation. \par
		Murphy et al. \cite{Murphy2009} presented a framework named Amsterdam for the automated application of metamorphic testing. The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file. Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.
		\subsubsection{Application domains}
		To answer the second question the authors selected the papers where the main objective was a case study. They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems. They also found some other domains of application like financial software, optimization programs, and encryption programs.
		Some of the research challenges identified by the authors are:
		\begin{itemize}
			\item Lack of guidelines, with step–by–step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
			\item Prioritisation and minimisation of metamorphic relations: It is worth mentioning that test case minimisation is a NP–hard problem and therefore heuristic techniques should be explored.
			\item Generation of likely metamorphic relations.
			\item Combination of metamorphic relations.
			\item Automated generation of best possible source test cases.
			\item Lack of metamorphic testing tools.
		\end{itemize}

	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
		In this paper the authors have demonstrated the usefulness of metamorphic testing in assessing the quality of applications without test oracles. Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format. The authors presented an approach called ``Automated Metamorphic System Testing'' to automate the metamorphic testing by considering the system as a blackbox and checking if the metamorphic properties holds after execution of the system. They also present another approach “Heuristic Metamorphic Testing” to reduce false positives and address some non-determinism. Unlike in the previous papers, here, the authors are focusing to improve the metamorphic testing technique itself. They list some benefits of using metamorphic testing: it can be used on broader domain of applications that display metamorphic properties, and it treats the application under test as a black box and does not require detailed understanding of the source code. They then list some of the limitations of using metamorphic testing:
		\begin{itemize}
			\item	Manual transformation of large input data can be laborious and error-prone. They need special tools to transform the input.
			\item Comparing the outputs(some of which may be very large and/or in not human-readable format) of the input data can be tedious.
			\item Floating point calculations can also lead to imprecision even though the calculations are programmatically correct.
			\item Coming up with the initial test-cases is also a challenge as some defects may only occur under certain inputs.
		\end{itemize}

		Automated Metamorphic System Testing: This technique can be used to test the application in development environment as well as in production as long as the users are only provided the output from the original execution and not the result from transformed input. In this model $i)$ Metamorphic properties are specified by the tester and applied to the input. $ii)$ The original input is fed into the application which is treated as a black-box and a transformation of the input is also generated. $iii)$ That transformed input is fed into a separate instance of the application running in a separate sandbox. $iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
		Tester need not write any code and only needs to specify the metamorphic properties. They don’t need to know the source code or other implementation details.
		Amsterdam framework: The metamorphic properties are specified using XML file. The specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.\par
		Heuristic Metamorphic testing: This method allows for small differences in outputs, in a meaningful way according to the application being used to address the problems of false positives and non-determinism. Imprecisions in floating point calculation and representation of irrational number such as may result in failure of metamorphic testing even if the implementation is correct. If two outputs are close enough they are considered the same. The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.

>>>>

\section{Metamorphic Testing}

In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. It is almost impossible to generate all the possible combinations of test cases to completely test a program which is why a lot of research is being conducted to develop more error-revealing test case selection strategies. A test case is called error-revealing if it is able to detect an error in the software otherwise it is labeled successful. Successful test case are the cases for which the program successfully computes the correct output. Since these test cases do not reveal any error, they are considered less important and are often not investigated further or, set aside for regression testing. {Zhou et al. (Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H. Huang‡, T.H. Tse§, Zongyuan Yang ¶, Haitao Huang ¶, and T. Y. Chen ‡)(Metamorphic testing and beyond) }

Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem. Metamorphic testing reuses successful test cases to generate followup test cases according to metamorphic relations whose output can easily be predicted. A metamorphic relation(MR) is an expected relation among input and outputs of multiple executions of the target program(Metamorphic testing and beyond)(METRIC: METamorphic Relation Identification based on the Category - choice framework). To formally define MRs we can assume a function $f$ which produces the output $f(x)$ on input $x$. The MRs of the function can then be used to generate a transformation function $t$, which, when applied to input $x$ produces $t(x)$. This transformed input can then be run through the function $f$ and the transformation allows us to predict the value of $f(t(x))$(Automatic system testing of programs without test oracle). 
A simple example of a MR would be a program that calculates mean of a set of numbers. Certain transformations of the set of numbers will result in the same value for mean like: permuting the order of numbers, since, this neither changes the number of elements in the set nor the value of any element. Another transformation that can be used would be multiplying each number in the set with -1. The new mean will be the negative value of the previous mean.

System under test(SUT)

\subsection{Properties of a good metamorphic relation}
Segura et al. did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing. They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems. They also found some other domains of application like financial software, optimization programs, and encryption programs.

They first studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
\begin{itemize}
	\item A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.
	\item Metamorphic relations that make execution of the follow-up test case as different as possible from the source test case.
	\item Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.
	\item Formally described metamorphic relations. In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow-up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
\end{itemize}

It should be noted that MT does not check the correctness of individual outputs. Instead, it checks the relations among several executions. Since no manual output predictions and comparisons are required, MT can be efficient and fully automated. \cite{Segura2016} The execution of a metamorphic test case is typically performed in two steps. First, a follow-up test case is generated by applying a transformation to the inputs of a source test case. Second, source and follow-up test cases are executed, checking whether their outputs violate the metamorphic relation. \par
	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
	A number of frameworks have been developed to automate the process of metamorphic testing. Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations. Given the source code of a program written in C and a metamorphic relation, AMT tries to find test cases that violate the relation. The underlying method is based on the translation of the code into an equivalent constraint logic program over finite domains. Other techniques like “special values” and random testing can also be used as source test cases for metamorphic testing. Genetic algorithms have also been used for the selection of source test cases, to maximize the paths traversed in the program under test.

		In this paper the authors have demonstrated the usefulness of metamorphic testing in assessing the quality of applications without test oracles. Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format. The authors presented an approach called ``Automated Metamorphic System Testing'' to automate the metamorphic testing by considering the system as a blackbox and checking if the metamorphic properties holds after execution of the system. They also present another approach “Heuristic Metamorphic Testing” to reduce false positives and address some non-determinism. Unlike in the previous papers, here, the authors are focusing to improve the metamorphic testing technique itself. They list some benefits of using metamorphic testing: it can be used on broader domain of applications that display metamorphic properties, and it treats the application under test as a black box and does not require detailed understanding of the source code. \cite{Murphy2009}

		\cite{Segura2016} Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively. In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow-up test case of each metamorphic relation as the source test case of the next metamorphic relation. \par
		Murphy et al. \cite{Murphy2009} presented a framework named Amsterdam for the automated application of metamorphic testing. The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file. Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.

		Automated Metamorphic System Testing: This technique can be used to test the application in development environment as well as in production as long as the users are only provided the output from the original execution and not the result from transformed input. In this model $i)$ Metamorphic properties are specified by the tester and applied to the input. $ii)$ The original input is fed into the application which is treated as a black-box and a transformation of the input is also generated. $iii)$ That transformed input is fed into a separate instance of the application running in a separate sandbox. $iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
		Tester need not write any code and only needs to specify the metamorphic properties. They don't need to know the source code or other implementation details.
		Amsterdam framework: The metamorphic properties are specified using XML file. The specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.\par
		Heuristic Metamorphic testing: This method allows for small differences in outputs, in a meaningful way according to the application being used to address the problems of false positives and non-determinism. Imprecision in floating point calculation and representation of irrational number such as may result in failure of metamorphic testing even if the implementation is correct. If two outputs are close enough they are considered the same. The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.\cite{Murphy2009}

Although metamorphic testing presents a lot of opportunities to expand on the existing testing processes, they also have some limitations. They then list some of the limitations of using metamorphic testing: \cite{Murphy2009}
		\begin{itemize}
			\item	Manual transformation of large input data can be laborious and error-prone. They need special tools to transform the input.
			\item Comparing the outputs(some of which may be very large and/or in not human-readable format) of the input data can be tedious.
			\item Floating point calculations can also lead to imprecision even though the calculations are programmatically correct.
			\item Coming up with the initial test-cases is also a challenge as some defects may only occur under certain inputs.
		\end{itemize}

		Some of the research challenges identified by the authors are:{A Survey on Metamorphic Testing \cite{Segura2016}}
		\begin{itemize}
			\item Lack of guidelines, with step-by-step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
			\item Prioritisation and minimisation of metamorphic relations: It is worth mentioning that test case minimisation is a NP-hard problem and therefore heuristic techniques should be explored.
			\item Generation of likely metamorphic relations.
			\item Combination of metamorphic relations.
			\item Automated generation of best possible source test cases.
			\item Lack of metamorphic testing tools.
		\end{itemize}
